Analyses for JSLHR version

### 2020-10-27 202010_jslhr/analyses.Rmd
coded chunk-based analyses

Using the Zooniverse annotations, we found that the association with age was very weak for children diagnosed with Angelman Syndrome r(`r myn["z_lp","AS"]`) = `r myr["z_lp","AS"]`, CI [`r mylb["z_lp","AS"]`,`r myhb["z_lp","AS"]`], p=`r myp["z_lp","AS"]`]; whereas younger low-risk control children showed a significant increase with age r(`r myn["z_lp","LR"]`) = `r myr["z_lp","LR"]`, CI [`r mylb["z_lp","LR"]`,`r myhb["z_lp","LR"]`], p=`r myp["z_lp","LR"]`]. Similarly, there were non-significant developmental decreases in the Canonical among children with Angelman Syndrome r(`r myn["z_cp","AS"]`) = `r myr["z_cp","AS"]`, CI [`r mylb["z_cp","AS"]`,`r myhb["z_cp","AS"]`], p=`r myp["z_cp","AS"]`]; and marginal developmental increases among low-risk control children, r(`r myn["z_cp","LR"]`) = `r myr["z_cp","LR"]`, CI [`r mylb["z_cp","LR"]`,`r myhb["z_cp","LR"]`], p=`r myp["z_cp","LR"]`].

Given that these derived metrics are defined at the child level, there was one stage in our pre-processing that may not have been necessary, whereby we collapsed judgments across chunks associated to the same segment. We therefore repeated our analyses but deriving our proportions for the Zooniverse data not from the segment-level composite, but rather the individual chunk-level annotations. We found that the Linguistic proportion was not strongly associated with age in the Angelman Syndrome group [r(8) = -.04, CI -.6 .6, p=0.91], but increased with age  in the low-risk control group [r(8) = .71, CI .15 .92, p=.02]. Similarly, the Canonical proportion did not exhibit the same pattern across the groups, with developmental decreases found among children with Angelman Syndrome r(8) = -.35, CI -.80 .35, p=.32; and developmental increases among low-risk control r(8) = .57, CI -.08 0.88, p=.83.

@@

```{r}
mygac=gac(data = sample_data, kat = 5, weight = c("unweighted"),
    conf.level = 0.95)

@@

When we use chunk-level judgments to derive the our child-level metrics, we observe very similar levels of correlation: linguistic proportion overall r (18) = .84, CI .63 .93, p<0.001 [Angelman Syndrome r(8) = .82, CI .41 .95, p<0.01; low-risk control r(8) = .84, CI .44 0.96, p<0.01]; canonical proportion overall r (18) = .96, CI .90 .98, p<0.001 [Angelman Syndrome r(8) = .85, CI .49 .85, p<0.01; low-risk control r(8) = .97, CI .89 .99, p<0.001].

>>>>

Using the Zooniverse annotations, we found that the association with age was very weak for children diagnosed with Angelman Syndrome r(`r myn["z_lp","AS"]`) = `r myr["z_lp","AS"]`, CI [`r mylb["z_lp","AS"]`,`r myhb["z_lp","AS"]`], p=`r myp["z_lp","AS"]`]; whereas younger low-risk control children showed a significant increase with age r(`r myn["z_lp","LR"]`) = `r myr["z_lp","LR"]`, CI [`r mylb["z_lp","LR"]`,`r myhb["z_lp","LR"]`], p=`r myp["z_lp","LR"]`]. Similarly, there were non-significant developmental decreases in the Canonical among children with Angelman Syndrome r(`r myn["z_cp","AS"]`) = `r myr["z_cp","AS"]`, CI [`r mylb["z_cp","AS"]`,`r myhb["z_cp","AS"]`], p=`r myp["z_cp","AS"]`]; and marginal developmental increases among low-risk control children, r(`r myn["z_cp","LR"]`) = `r myr["z_cp","LR"]`, CI [`r mylb["z_cp","LR"]`,`r myhb["z_cp","LR"]`], p=`r myp["z_cp","LR"]`].
```{r bychunk-age}
read.csv("../Derived_Data/chunk_majority_agreement_1751.csv")->chunk
bychild=table(chunk$Answer,chunk$ChildID)
cans=bychild["Canonical",]
noncans=bychild["Non-Canonical",]
junk=bychild["Junk",]
sum_bychild=table(chunk$ChildID)

ling_prop=(cans+noncans)/(sum_bychild-junk)
can_prop=cans/(cans+noncans)

demo_data$ChildID==names(ling_prop)
demo_data$ChildID==names(can_prop)

props_bychild_chunk=cbind(ling_prop,can_prop,demo_data)
colnames(props_bychild_chunk)[1:2]<-c("chi","ling_prop")

z_lp_as=cor.test(props_bychild_chunk$ling_prop[props_bychild_chunk$Diagnosis=="AngelmanSyndrome"],props_bychild_chunk$Age[props_bychild_chunk$Diagnosis=="AngelmanSyndrome"])

z_lp_lr=cor.test(props_bychild_chunk$ling_prop[props_bychild_chunk$Diagnosis!="AngelmanSyndrome"],props_bychild_chunk$Age[props_bychild_chunk$Diagnosis!="AngelmanSyndrome"])

z_cp_as=cor.test(props_bychild_chunk$can_prop[props_bychild_chunk$Diagnosis=="AngelmanSyndrome"],props_bychild_chunk$Age[props_bychild_chunk$Diagnosis=="AngelmanSyndrome"])

z_cp_lr=cor.test(props_bychild_chunk$can_prop[props_bychild_chunk$Diagnosis!="AngelmanSyndrome"],props_bychild_chunk$Age[props_bychild_chunk$Diagnosis!="AngelmanSyndrome"])
```

Given that these derived metrics are defined at the child level, there was one stage in our pre-processing that may not have been necessary, whereby we collapsed judgments across chunks associated to the same segment. We therefore repeated our analyses but deriving our proportions for the Zooniverse data not from the segment-level composite, but rather the individual chunk-level annotations. We found that the Linguistic proportion was not strongly associated with age in the Angelman Syndrome group: r(`r z_lp_as$parameter`) = `r z_lp_as$estimate`, CI [`r z_lp_as$conf.int[1]`,`r z_lp_as$conf.int[2]`], p=`r z_lp_as$p.value`], but increased with age  in the low-risk control group: r(`r z_lp_lr$parameter`) = `r z_lp_lr$estimate`, CI [`r z_lp_lr$conf.int[1]`,`r z_lp_lr$conf.int[2]`], p=`r z_lp_lr$p.value`. Similarly, the Canonical proportion did not exhibit the same pattern across the groups, with developmental decreases found among children with Angelman Syndrome r(`r z_cp_as$parameter`) = `r z_cp_as$estimate`, CI [`r z_cp_as$conf.int[1]`,`r z_cp_as$conf.int[2]`], p=`r z_cp_as$p.value`]; and developmental increases among low-risk control r(`r z_cp_lr$parameter`) = `r z_cp_lr$estimate`, CI [`r z_cp_lr$conf.int[1]`,`r z_cp_lr$conf.int[2]`], p=`r z_cp_lr$p.value`.

@@

```{r mygac-conf}
mygac=gac(data = sample_data, kat = 5, weight = c("unweighted"),
    conf.level = 0.95)

@@

```{r zoo-lab-chunk}

proportions=proportions[order(proportions$ChildID),]

  #get cor properties
  thiscor=cor.test(props_bychild_chunk[props_bychild_chunk$Diagnosis=="AngelmanSyndrome","ling_prop"],proportions[proportions$Diagnosis=="AngelmanSyndrome","l_lp"])
    myr[1,"AS"]=round(thiscor$estimate,3)
    mylb[1,"AS"]=round(thiscor$conf.int[1],3)
    myhb[1,"AS"]=round(thiscor$conf.int[2],3)
    myn[1,"AS"]=round(thiscor$parameter,3)
    myp[1,"AS"]=round(thiscor$p.value,3)

  #repeat for LR

      #get cor properties
  thiscor=cor.test(props_bychild_chunk[props_bychild_chunk$Diagnosis!="AngelmanSyndrome","ling_prop"],proportions[proportions$Diagnosis!="AngelmanSyndrome","l_lp"])
    myr[1,"LR"]=round(thiscor$estimate,3)
    mylb[1,"LR"]=round(thiscor$conf.int[1],3)
    myhb[1,"LR"]=round(thiscor$conf.int[2],3)
    myn[1,"LR"]=round(thiscor$parameter,3)
    myp[1,"LR"]=round(thiscor$p.value,3)

      thiscor=cor.test(props_bychild_chunk$ling_prop,proportions$l_lp)
    myr[1,"all"]=round(thiscor$estimate,3)
    mylb[1,"all"]=round(thiscor$conf.int[1],3)
    myhb[1,"all"]=round(thiscor$conf.int[2],3)
    myn[1,"all"]=round(thiscor$parameter,3)
    myp[1,"all"]=round(thiscor$p.value,3)

  #get cor properties
  thiscor=cor.test(props_bychild_chunk[props_bychild_chunk$Diagnosis=="AngelmanSyndrome","can_prop"],proportions[proportions$Diagnosis=="AngelmanSyndrome","l_cp"])
    myr[2,"AS"]=round(thiscor$estimate,3)
    mylb[2,"AS"]=round(thiscor$conf.int[1],3)
    myhb[2,"AS"]=round(thiscor$conf.int[2],3)
    myn[2,"AS"]=round(thiscor$parameter,3)
    myp[2,"AS"]=round(thiscor$p.value,3)

  #repeat for LR

      #get cor properties
  thiscor=cor.test(props_bychild_chunk[props_bychild_chunk$Diagnosis!="AngelmanSyndrome","can_prop"],proportions[proportions$Diagnosis!="AngelmanSyndrome","l_cp"])
    myr[2,"LR"]=round(thiscor$estimate,3)
    mylb[2,"LR"]=round(thiscor$conf.int[1],3)
    myhb[2,"LR"]=round(thiscor$conf.int[2],3)
    myn[2,"LR"]=round(thiscor$parameter,3)
    myp[2,"LR"]=round(thiscor$p.value,3)

      thiscor=cor.test(props_bychild_chunk$can_prop,proportions$l_cp)
    myr[2,"all"]=round(thiscor$estimate,3)
    mylb[2,"all"]=round(thiscor$conf.int[1],3)
    myhb[2,"all"]=round(thiscor$conf.int[2],3)
    myn[2,"all"]=round(thiscor$parameter,3)
    myp[2,"all"]=round(thiscor$p.value,3)
```

When we use chunk-level judgments to derive the our child-level metrics, we observe very similar levels of correlation: linguistic proportion overall r(`r myn["lp","all"]`) = `r myr["lp","all"]`, CI [`r mylb["lp","all"]`,`r myhb["lp","all"]`], p=`r myp["lp","all"]`] between Linguistic proportion by child from the Zooniverse and the lab annotators' data.  When we split by participant group, correlations remain high: for Angelman Syndrome r(`r myn["lp","AS"]`) = `r myr["lp","AS"]`, CI [`r mylb["lp","AS"]`,`r myhb["lp","AS"]`], p=`r myp["lp","AS"]`]; low-risk control r(`r myn["lp","LR"]`) = `r myr["lp","LR"]`, CI [`r mylb["lp","LR"]`,`r myhb["lp","LR"]`], p=`r myp["lp","LR"]`]. As for canonical proportion overall r(`r myn["cp","all"]`) = `r myr["cp","all"]`, CI [`r mylb["cp","all"]`,`r myhb["cp","all"]`], p=`r myp["cp","all"]`; Angelman Syndrome: r(`r myn["cp","AS"]`) = `r myr["cp","AS"]`, CI [`r mylb["cp","AS"]`,`r myhb["cp","AS"]`], p=`r myp["cp","AS"]`];  low-risk control infants r(`r myn["cp","LR"]`) = `r myr["cp","LR"]`, CI [`r mylb["cp","LR"]`,`r myhb["cp","LR"]`], p=`r myp["cp","LR"]`.
